cvx-flats

### 2020-05-11 neurips-20/cvx-flats-statements.tex
Added proof of Lemma 1

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}

@@

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$ with $r \in \gamma(p)$.
	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  \jessie{...}
  \raf{Time to take a crack}
\end{proof}

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}

@@

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  To spell it out, observe $F-p$ is a subspace as it is a linear transformation of $F$, which is a subspace by definition of a flat.

  Now consider $q \in F - p$.
  First, if $p+q \in \gamma_r$ and $p -q \in \gamma_r$, then we have $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
  If either $p + q$ or $p - q \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.

  However, if both $p + \alpha^+ q$ and $p - \alpha^- q \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $q \not \in F - p$.
  Therefore, we have $q \in F - p \implies q \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
\end{proof}
